Same as always: I suck at titles

### 2024-09-27 manuscript/manuscript_eb.Rmd
minor changes

In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent. We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently. If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners’ lower FOAK for the speaker. However, disfluent descriptions provided by a non-native speaker may not impact listeners’ betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker’s knowledge. To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker [see @dragojevicgiles2016], perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived reliability of each speaker. We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements [@boduchlevari2021].

@@

In our pre-registration, we stipulated that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could partake in the study. Further, we would exclude from analysis data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four, or considered themselves experts in horse races. This meant that we recruited 641 participants for a sample of 360. Participants were recruited via the online platform Prolific, and gave their informed consent as approved by the PPLS Ethics Committee (ref no 133-2223/3). Participants were reimbursed £1.50 for a 10-minutes experiment.

@@

Stimuli were presented using JsPsych [@jspsych], hosted on MindProbe [via JATOS, @jatos]. The task began with a cover story introducing two horse racing tipsters. Participants were told the tipsters would provide information about the four most popular horses competing in an upcoming race at Musselburgh Racecourse (Edinburgh). The cover story explained that the two tipsters were well-known experts in the field, and added that one of the speakers was a non-native English speaker (without specifying the nationality of either speaker), introducing the element of the speakers' linguistic backgrounds as well as the factor of competence.

@@

All data pre-processing and analyses were carried out in R version 4.4.1 [@R-base], using the packages _tidyverse_ version 2.0.0 [@tidyverse], _ggplot_ version 3.5.1 [@ggplot2], and _wesanderson_ version for data wrangling and visualization. _lme4_ version 1.1-35.5 [@lme4] was used for data analysis, and _papaja_ version 0.1.2 [@R-papaja] for manuscript write-up. Scripts can be found at https://osf.io/zsut7/

@@

Table \@ref(tab:tab-dist-money) and Figure \@ref(fig:fig1) show the mean amount of money bet per speaker and fluency condition. On average, participants bet £25 on when information was provided fluently. This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally. However, disfluent instructions seem to lower the amount of money bet.

@@

```{r fig1, out.width="90%",fig.align='center', fig.cap="Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native)."}
fig1
```

@@

### Language attitudes

>>>>

In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent. We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently. If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners’ lower trust in, or lower FOAK, for the speaker. However, disfluent descriptions provided by a non-native speaker may not impact listeners’ betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker’s knowledge. To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker [see @dragojevicgiles2016], perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived trustworthiness of each speaker. We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements [@boduchlevari2021].

@@

In our pre-registration, we stipulated that only participants born and raised, and currently residing in the United Kingdom, with English as their first and only language, and with no auditory disorders could partake in the study. Further, we would exclude from analysis data from participants who reported the experiment's aim or manipulation, rated the naturalness of the auditory stimuli (defined as how likely they believed the audios to have been recorded in one go) lower than four, or considered themselves experts in horse races. This meant that we recruited 641 participants for a sample of 360. Participants were aged between 18 and 30, born and raised in the United Kingdom, and reported that they did not consider themselves as experts in horse races. Participants were recruited via the online platform Prolific, and gave their informed consent as approved by the PPLS Ethics Committee (ref no 133-2223/3). Participants were reimbursed £1.50 for a 10-minutes experiment.

@@

Stimuli were presented using JsPsych [@jspsych], hosted on MindProbe [via JATOS, @jatos]. The task began with a cover story introducing two horse racing tipsters. Participants were told the tipsters would provide information about the four most popular horses competing in an upcoming race. The cover story explained that the two tipsters were well-known experts in the field, and added that one of the speakers was a non-native English speaker (without specifying the nationality of either speaker), introducing the element of the speakers' linguistic backgrounds as well as the factor of competence.

@@

All data pre-processing and analyses were carried out in R version 4.4.1 [@R-base], using the packages _tidyverse_ version 2.0.0 [@tidyverse], _ggplot_ version 3.5.1 [@ggplot2], and _wesanderson_ version 0.3.7 for data wrangling and visualization. _lme4_ version 1.1-35.5 [@lme4] was used for data analysis, and _papaja_ version 0.1.2 [@R-papaja] for manuscript write-up. Scripts can be found at https://osf.io/zsut7/

@@

Table \@ref(tab:tab-dist-money) shows the mean amount of money bet per speaker and fluency condition. On average, participants bet £25 on when information was provided fluently. This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally. However, disfluent instructions seem to lower the amount of money bet.

@@

@@

### Language attitudes and post-experimental questionnaire

### 2024-09-27 manuscript/manuscript_eb.tex
minor changes

In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent. We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently. If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners' lower FOAK for the speaker. However, disfluent descriptions provided by a non-native speaker may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge. To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker (see Dragojevic \& Giles, 2016), perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived reliability of each speaker. We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements (Boduch-Grabka \& Lev-Ari, 2021).

@@

Stimuli were presented using JsPsych (Leeuw, Gilbert, \& Luchterhandt, 2023), hosted on MindProbe (via JATOS, Lange, Kühn, \& Filevich, 2015). The task began with a cover story introducing two horse racing tipsters. Participants were told the tipsters would provide information about the four most popular horses competing in an upcoming race at Musselburgh Racecourse (Edinburgh). The cover story explained that the two tipsters were well-known experts in the field, and added that one of the speakers was a non-native English speaker (without specifying the nationality of either speaker), introducing the element of the speakers' linguistic backgrounds as well as the factor of competence.

@@

All data pre-processing and analyses were carried out in R version 4.4.1 (R Core Team, 2024), using the packages \emph{tidyverse} version 2.0.0 (Wickham et al., 2019), \emph{ggplot} version 3.5.1 (Wickham, 2016), and \emph{wesanderson} version for data wrangling and visualization. \emph{lme4} version 1.1-35.5 (Bates, Mächler, Bolker, \& Walker, 2015) was used for data analysis, and \emph{papaja} version 0.1.2 (Aust \& Barth, 2023) for manuscript write-up. Scripts can be found at \url{https://osf.io/zsut7/}

@@

Table \ref{tab:tab-dist-money} and Figure \ref{fig:fig1} show the mean amount of money bet per speaker and fluency condition. On average, participants bet £25 on when information was provided fluently. This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally. However, disfluent instructions seem to lower the amount of money bet.

@@

\begin{figure}[H]

{\centering \includegraphics[width=0.9\linewidth,]{manuscript_eb_files/figure-latex/fig1-1}

\caption{Money distribution by manner of delivery (fluent/disfluent) and speaker (green: native/orange: non-native).}\label{fig:fig1}
\end{figure}

@@

\hypertarget{language-attitudes}{%
\subsubsection{Language attitudes}\label{language-attitudes}}

>>>>

In a pre-registered study, we set up to explore whether and how perceptions of certainty are biased by manner of delivery in the form of fluency, and by the speaker's identity as conveyed by their accent. We presented participants with recordings of a native and a non-native speaker, each describing two horses, with one description produced fluently and one description produced disfluently. If listeners are sensitive to both local and global causes of hesitations when making judgements about certainty, then disfluent descriptions provided by a native speaker should result in less money bet, reflecting listeners' lower trust in, or lower FOAK, for the speaker. However, disfluent descriptions provided by a non-native speaker may not impact listeners' betting behaviours, to the extent that they consider the possibility of difficulties in production when assessing the speaker's knowledge. To further control for the potential effects of (non)-nativeness on certainty on its own, we measured participants' language attitudes towards each speaker (see Dragojevic \& Giles, 2016), perceived fluency, accentedness, and comprehensibility of the native and the non-native speaker, as well as the perceived trustworthiness of each speaker. We additionally measured participants' familiarity with and exposure to native and non-native-accented English on a daily basis, to account for the fact that exposure to non-native accents can reduce their negative effects on listeners' judgements (Boduch-Grabka \& Lev-Ari, 2021).

@@

Stimuli were presented using JsPsych (Leeuw, Gilbert, \& Luchterhandt, 2023), hosted on MindProbe (via JATOS, Lange, Kühn, \& Filevich, 2015). The task began with a cover story introducing two horse racing tipsters. Participants were told the tipsters would provide information about the four most popular horses competing in an upcoming race. The cover story explained that the two tipsters were well-known experts in the field, and added that one of the speakers was a non-native English speaker (without specifying the nationality of either speaker), introducing the element of the speakers' linguistic backgrounds as well as the factor of competence.

@@

All data pre-processing and analyses were carried out in R version 4.4.1 (R Core Team, 2024), using the packages \emph{tidyverse} version 2.0.0 (Wickham et al., 2019), \emph{ggplot} version 3.5.1 (Wickham, 2016), and \emph{wesanderson} version 0.3.7 for data wrangling and visualization. \emph{lme4} version 1.1-35.5 (Bates, Mächler, Bolker, \& Walker, 2015) was used for data analysis, and \emph{papaja} version 0.1.2 (Aust \& Barth, 2023) for manuscript write-up. Scripts can be found at \url{https://osf.io/zsut7/}

@@

Table \ref{tab:tab-dist-money} shows the mean amount of money bet per speaker and fluency condition. On average, participants bet £25 on when information was provided fluently. This distribution suggests that participants followed a rational behaviour: Given their lack of expertise, they distributed the one hundred pounds equally. However, disfluent instructions seem to lower the amount of money bet.

@@

@@

\hypertarget{language-attitudes-and-post-experimental-questionnaire}{%
\subsubsection{Language attitudes and post-experimental questionnaire}\label{language-attitudes-and-post-experimental-questionnaire}}
